\large{\bf Looking forwards and backwards: dynamics and genealogies of locally regulated populations }

### 2023-12-06 review-responses.tex

%%%%%%
%%
%%  Don't reorder the reviewer points; that'll mess up the automatic referencing!
%%
%%%%%

\begin{minipage}[b]{2.5in}
  Resubmission Cover Letter \\
  {\it Theoretical Population Biology}
\end{minipage}
\hfill
\begin{minipage}[b]{2.5in}
    Peter Ralph \\
  \today
\end{minipage}

\vskip 2em

\noindent
{\bf To the Editor(s) -- }

\vskip 1em

We are writing to submit a revised version of our manuscript,
ETCETERA

\vskip 2em

\noindent \hspace{4em}
\begin{minipage}{3in}
\noindent
{\bf Sincerely,}

\vskip 2em

{\bf 
Peter Ralph
}\\
on behalf of \\
{\bf 
Alison Etheridge,
Tom Kurtz,
Ian Letter,
and Terence Tsui Ho Lung.
}\\
\end{minipage}

\vskip 4em

\pagebreak

%%%%%%%%%%%%%%
\section*{AE comments:}

%%%%%%%%%%%%%%
\reviewersection{1}

\begin{quote}
The authors introduced a class of spatial population models in which individuals have locations
in the continuum space $\IR^d$. The population dynamics is controlled by three quantities: birth,
establishment and death, each of which can depend on the spatial location and local population
density. For a fixed time $t$, the population can be represented by a point measure $\eta_t^N$ in which
each individual is assigned a mass $1/N$, where $N$ is a parameter such that initially there are $O(N)$
individuals per unit volume in $\IR^d$. The population dynamics is represented by a continuous-time
Markov process $(\eta_t^N)_{t\ge0}$. The key feature of this model is that it distinguishes between juveniles
and adults. The authors obtained three different scaling limits for the model $(\eta_t^N)_{t\ge0}$ as $N \to \infty$,
which are super-processes, non-local differential equation and reaction-diffusion type PDE. The
author also obtained a description of the dynamics of a single lineage as $N \to \infty$, when the
limiting population dynamics is deterministic.

A main contribution of this paper is the rigorous derivation of lineage dynamics through the
lookdown construction. The convergence of the population dynamics to super-processes, non-
local PDE and PDE are also significant, as they inform us of not only the limiting object that are
expected to be robust against model perturbation, but also of the corresponding scaling regimes
and parameter combinations for model reduction. The one-step convergence presents a usual technical
challenge about identifying the limit. The authors overcame the challenge masterfully by
establishing continuity estimates that guarantee good agreement for the nonlinear terms between
the limiting PDE and the stochastic model, under high mixing rate and a high density assumption.
Overall, this is a very high quality paper that contains many interesting and novel results to merit
publication in EJP, after minor revision.
\end{quote}

Thanks ETCETERA

\subsection*{Major comments}

\begin{point}{\revref}
The first paragraph seems sloppy. For example, this expression [for $\mu_\theta(x)$] is non-negative for
what range of values for $(x, \eta)$? Why ``anyway true for sufficiently large $\theta$''? Perhaps this
assumption should be labeled and called upon whenever is it being referred to.
\end{point}

\reply{
}

\begin{point}{\revref}
Definition \ref{def:lineage_generator}, Proposition 2.23: I think these may need to be rewritten/rephrased. Up
to Proposition \ref{thm:lineages}, it is not clear what ``that individual'' is in the limiting model. Therefore,
it is not clear what $L_s$ is. While the definition of the process $L^N$ maybe clear, what is the
precise definition of $L_s$ ? I think these need to be defined through the finite-$N$ models. It may
be good to explain why the process $L$ is Markovian, or at least point out that it is Markovian,
before talking about semigroup. Probably Section \ref{sec:lineage_motion} will need to be modified accordingly.
\end{point}

\reply{
}

\begin{point}{\revref}
The two conditions in equation \eqref{conditions for one step} are crucial for the one-step convergence.
It would be great to mention exactly where each of them are used in Section \ref{subsec:one step convergence proof}.
A brief explanation about these conditions would also be nice. For example, it seems the first (high
migration/mixing rate) condition in \eqref{conditions for one step},
but not the second (high density) condition, is used
to guarantees that $\psi_t^{\epsilon,x}$ is close to a heat kernel?
\end{point}

\reply{
}

\subsection*{Minor comments}

\begin{point}{\revref}
\eqref{eqn:mu_defn}: The authors mentioned ``define the death rate'' and ``where this equation defines F'',
which is confusing. What is being defined here? Please clarify. It seems to me that one has
to first choose $F$, then define $µ_\theta(x)$ as in \eqref{eqn:mu_defn}.
\end{point}

\reply{
}

\begin{point}{\revref}
% P7, paragraph after Remark 2.3:
``and once there establishes...'' It maybe better to split this
long sentence into two complete sentences.
\end{point}

\reply{
}

\begin{point}{\revref}
% P7, paragraph after Remark 2.3:
$\meanq(x)$ and $\covq(x)$ did not appear before. Perhaps mention they
are given/chosen, or simply delete them here, and mention them in Definition \ref{def:dispersal_generator}.
\end{point}

\reply{
}

\begin{point}{\revref}
Remark \ref{ancestral lineages: first guess}
Why use $m$ in the superscript of $q_\theta^m(x, \eta, dy)$?
\end{point}

\reply{
}

\begin{point}{}
Assumptions \ref{def:model_setup}: Should it be ``Assumption 2.8'' instead? Also, $\alpha$ in condition 1 was
used in $\alpha = lim_{N \to \infty} \theta(N)/N$ on Page 8, Figure 1, etc.
\end{point}

\reply{
}

\begin{point}{\revref}
% P9 last line:
    Should the ``$C$'' on the right hand side of the equal sign [in the equation for $C_f$] be deleted ?
\end{point}

\reply{
}

\begin{point}{\revref}
% P10 paragraph below Lemma 2.9:
    Why ``no longer suffices'', and why this is true? . Please
explain. I don’t seem to find this explained in any remark before this.
\end{point}

\reply{
}

\begin{point}{}
Figure 1: What is $N$, the time and other parameters (e.g. $\rho_r$ , $\rho_\gamma$) in the simulations? Same
for other figures. Please at least specify the range of values.
\end{point}

\reply{
}

\begin{point}{\revref}
% P12 paragraph after Corollary 2.11:
A more precise reference, or explanation for why
uniqueness holds for this special case would be helpful, as the references you ave are all
quite extensive.
\end{point}

\reply{
}

\begin{point}{}
Proposition \ref{nonlocalPME to PME}:
    It seems the constant $C$ is not needed. Perhaps just say the supremum
of the first displayed expression over $\epsilon$ finite?
\end{point}

\reply{
}

\begin{point}{}
Remark \ref{remark_on_nonlocal_to_local}: Can you explain a bit more why it will be necessary to retain averaging of r?
\end{point}

\reply{
}

\begin{point}{\revref}
% P16: Second paragraph:
The notation $L_t$ seems to first appear here and was not yet defined.
\end{point}

\reply{
    (Note: they said ``P16: Second paragraph''; I think they just missed it on the previous page.)
}

\begin{point}{}
% P19-20:
    The equations for the lineage dynamics for the three examples [i.e., Fisher-KPP \revref, Allen-Cahn, and Porous Medium] are interesting.
Which is/are new in this paper, and which was/were known before (and related references)?
\end{point}

\reply{
}

\begin{point}{}
This maybe out of the scope of this paper, but it is related. As the authors pointed out, two
lineages probably will not coalesce in the limiting model. However, they will coalesce in
the finite-$N$ model, though it may take a very long time. I wonder if the authors have a
feeling about whether the description of the lineage dynamics in the limit still be a good
approximation for that of the finite model for such a long time.
\end{point}

\reply{
}

\begin{point}{}
The subtitle of section \ref{sec:nonunique_lineage} does not match the actual content in that section. Please
update the subtitle. Also, can you give a reference for the claim in the last sentence in this
section \revref?
\end{point}

\reply{
}

\begin{point}{\revref}
specify ``this process'' in the line below the first displayed equation in
Section 5.1.
\end{point}

\reply{
}

\begin{point}{\revref}
Paragraph starting with ``Levels never cross below 0'': Should it be instead ``Levels never
go above $N$''? If so, what particles are regarded as dead? Perhaps those exit the interval
$[0, N]$? Note that equation \eqref{eqn:dot_u} suggests that levels can now go above $N$.
\end{point}

\reply{
}

\begin{point}{\revref}
``Recall from equation~\eqref{eqn:mu_defn}''
does not seem correct, as there is a max in \eqref{eqn:mu_defn}. Please
correct this.
\end{point}

\reply{
}

\begin{point}{\revref}
Please give a precise reference/explanation to why uniqueness holds for the martingale problem for finite $N$.
\end{point}

\reply{
}

\begin{point}{\revref}
% P32 third line in Section 5.3:
    Pointwise in time?
\end{point}

\reply{
}

\begin{point}{\revref}
Proposition \ref{prop:limiting_construction}: In ``For any solution to the equation above'', what is a ``solution''? Is it
a solution for all time? Also, be specific to ``the equations above'' by labeling and referring
to the precise equations including the unlabeled displayed equation below \eqref{eqn:limiting_construction}.
\end{point}

\reply{
}

\begin{point}{\revref}
The word ``Proof'' is missing in ``Proof of Proposition 5.6''. This word is also
missing in other places in Sections 6-8.
\end{point}

\reply{
}

\begin{point}{}
``Proof of Proposition \ref{prop:limiting_construction}'': Do you also need the unlabeled displayed equation below
\eqref{eqn:limiting_construction}? The solution is for all time.
\end{point}

\reply{
}

\begin{point}{\revref}
Be specific about ``these results'' in ``Proof of the remainder of these results...'' Also, at the
very beginning of Remark \ref{remark_on_branching}, Be specific about what ``The process'' is.
\end{point}

\reply{
}

\begin{point}{\revref}
``Condition 1'' here is that for Lemma 2.9, not that for Assumptions 2.8. Please specify.
\end{point}

\reply{
}

\begin{point}{\revref}
Perhaps give a reference to the ``familiar pattern''.
\end{point}

\reply{
}

\begin{point}{\revref}
% P40 first displayed equation:
Mention $M_t$ is a martingale for all such test functions.
\end{point}

\reply{
}

\begin{point}{\revref}
%    P48:
    The notation $\mathcal{O}(\epsilon)$ seems to first appear here. Please explain its meaning. Do they
depend on x?
\end{point}

\reply{
}

\begin{point}{\revref}
% P54: near the bottom:
    Can you be more specific what in paper \citet{barlow/jacka/yor:1986} is being used here?
\end{point}

\reply{
}

\begin{point}{\revref}
% P60:
The notation $\mathcal{O}(\delta)$ seems to first appear here. Please explain its meaning. Do they
depend on x?
\end{point}

\reply{
}

\begin{point}{\revref}
% P65: Remark 8.1:
measure-values processes $\to$ measure-valued processes
\end{point}

\reply{
}

\begin{point}{}
Section \ref{sec:lineages_proof}8.2 may nned to be modified also based on the second point in ``Major
comments'' above.
\end{point}

\reply{
}

### 2023-12-06 forwards-and-backwards.tex
put in reviewer responses

@@

We shall write $\mu_\theta(x, X/N)$ for the per-capita death rate of mature individuals
in the population.
In order for the 
population density to change over timescales of order $\theta$, we should like the net 
per capita reproductive rate 
to scale as $1/\theta$. 
In classical models, in which $r$, $\gamma$, and $\mu$ are constant, 
this quantity is simply $r\gamma -\mu$. 
Here, because production of juveniles and their establishment are
mediated by population density measured relative to different points, 
the net reproductive rate will take a more complicated form. 
In particular, the total rate of production of mature offspring by an individual at $x$ will be
\begin{equation} \label{eqn:total_repro}
	\gamma\big(x,\smooth{\gamma}X(x)/N\big)\int r\big(y, \smooth{r}X(y)/N\big)q_{\theta}(x,dy).
\end{equation}
Nonetheless, it will be convenient to define the death rate $\mu_\theta$ in terms of 
its deviation from $r\gamma$. 
To this end, we define
the death rate of an individual at $x$ to be
\begin{align} \label{eqn:mu_defn}
    \mu_\theta(x)
    =
    \max\left\{0, 
        r(x, \smooth{r} X(x) / N) \gamma(x, \smooth{\gamma} X(x) / N)
        - \frac{1}{\theta} F(x, \smooth{F} X(x) / N)
    \right\} ,
\end{align}
where this equation defines $F(x, m) : \IR^d \times \IR_{\ge 0} \to \IR$,
and $\rho_F$ is again a smooth kernel. 
The function $F$ is nearly
the net per capita reproductive rate, scaled by $\theta$,
and would be equal to it in a nonspatial model;
but, as can be seen from \eqref{eqn:total_repro},
differs because an offspring's establishment probability is measured at their new location
rather than that of their parent.
For the most part, we work with $F$ instead of $\mu_\theta$.

@@

In summary, at each time $t$, $\eta^N_t$ is purely atomic, consisting of atoms of mass $1/N$
(which are the individuals).
At instantaneous rate $\theta \gamma(x, \eta^N_t) N \eta^N_t(dx)$ an offspring of mass $1/N$ is 
produced at location $x$; it disperses to 
a location $y$ offset from $x$
by an independent Gaussian random variable with mean $\meanq(x) / \theta$
and covariance matrix $\covq(x) / \theta$, and once there establishes instantaneously
with probability $r(y, \eta^N_t)$, or else dies. 
At instantaneous rate $\theta \mu_\theta(x, \eta^N_t) N \eta^N_t(dx)$ an individual at location 
$x$ dies.
Note that the process 
$\left(\eta^N_t\right)_{t\ge 0}$, which
records numbers and locations of adult individuals, is just a scaled spatial birth and 
death process. If, for example, we insist that $\gamma(x,m)$ is bounded, then 
existence (and in particular non-explosion) is guaranteed by comparison with
a pure birth process. We do not dwell on this, as we shall require more stringent conditions
if we are to pass to the limit as $\theta$ and $N$ tend to infinity.

@@

\begin{remark}
\label{ancestral lineages: first guess}
An equivalent way to describe the model would be to say that
when the state of the population is $\eta$,
an individual at $x$ gives birth at rate
$$
    \theta \gamma(x, \eta)
    \int r(y, \eta) q(x, dy) ,
$$
and that offspring disperse according to the kernel
$$
    q_\theta^\mathfrak{m}(x,\eta,dy)
    :=
    \frac{
        r(y, \eta) q_\theta(x, dy)
    }{
        \int r(z, \eta) q_\theta(x, dz)
    } .
$$
Clearly, the random walk driven by this dispersal kernel
is biased towards regions of higher establishment probability.
For comparison with future results,
it is interesting to write down the limiting generator:
\begin{align}
	\label{weighted dispersal}
    \lim_{\theta \to \infty}
    \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, \eta, dy)
    &=
    \frac{
        \DG\left[ f(\cdot) r(\cdot, \eta) \right](x)
        - 
        f(x) \DG\left[ r(\cdot, \eta) \right](x)
    }{
        r(x, \eta^{N})
    } .
\end{align}
In the simplest case of unbiased isotropic dispersal
(i.e.,~$\meanq = 0$ and $\covq = I$), $\DG = \Delta$,
and so~(\ref{weighted dispersal}) is equal to
\begin{align*}
    \Delta f(x) + 2 \grad f(x) \cdot \grad \log r(\cdot, \smooth{r} \eta(\cdot))(x) .
\end{align*}
One might guess that the spatial motion described by following  
the ancestral lineage of an individual 
back through time
would be described (in the limit) by the adjoint of this generator.
However, we will see in Section~\ref{sec:ancestral lineages}
that this is not in fact the case.
\end{remark}

@@

{\bf Reproduction parameters:}
We assume that 
\begin{enumerate}
            \addtocounter{enumi}{2}
\item The function $F(x,m)$ satisfies 
    \begin{enumerate}
    \item $F(x,m)$ is locally Lipschitz in $m$;
    \item $F(x,m)$ is uniformly bounded above (but not necessarily below);
    \item for each fixed $m$, $\sup_{x\in\IR^d}\sup_{k\leq m}|F(x,k)|<\infty$;
    \end{enumerate}
\item The functions $r(x,m)$, $\gamma(x,m)$ have bounded first and second 
    derivatives in both arguments;
    \label{r_gamma_derivs_condition}
\item $\gamma(x,m)$ is uniformly bounded;
    \label{gamma_bounded_condition}
\item For each $f \in C_b^2(\IR^d)$,
    there is a $C_f$ such that
    $$
        |\gamma(x, \eta) \theta \int 
        (r(y,\eta) f(y) - r(x, \eta) f(x))
        q_\theta(x, dy)| \le C_f (1 + |f(x)|)
    $$
    for all $x \in \IR^d$ and $\eta \in \measures$.
    Furthermore, $C_f$ only depends on the norm of the first two derivatives of $f$,
    i.e., 
    \[
        C_f = C(\sup_x \sup_{\|z\|=1} \max( \sum_i z_i \partial_{x_i} f(x), \sum_{ij} z_i z_j \partial_{x_i x_j} f(x))) .
    \] \label{gamma_B_condition}
\end{enumerate}
To keep expressions manageable, we shall also assume that 
\[
\mu_\theta(x) = r(x,\eta) \gamma(x,\eta) - \frac{1}{\theta} F(x,\eta),
\]
that is, this expression is non-negative so that there is no need to take the maximum
	with zero in~(\ref{eqn:mu_defn}). (This is anyway true for 
	sufficiently large $\theta$.)
\end{assumptions}

@@

The purpose of the conditions that we have placed on the reproduction parameters is to 
ensure that the net per capita reproduction rate (before time scaling)
is order $1/\theta$. As remarked above, 
because of the non-local reproduction mechanism, it no longer suffices to assume that 
$r(x,\eta)\gamma(x,\eta)-\mu_\theta(x)$ is of order $1/\theta$.
Perhaps the simplest example in which we can see this
is the case where $\gamma \equiv 1$ and $F \equiv 0$, so that $\mu_\theta = r$,
and $\eta = \delta_x$
(i.e., the population has all individuals at a single location),
so that $\smooth{r} \eta(y) = \rho_r(y)$.
In this case, the mean rate of change of the total population size
is $\int (r(y, \rho_r(y) ) - r(x, \rho_r(x))) q_\theta(x, dy)$;
the first condition of Lemma~\ref{lem:conditions on r} would ensure this is of order $1/\theta$.

@@

\begin{corollary} \label{cor:superprocess_uniqueness}
    Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
    if the martingale problem
    defined by equations~\eqref{eqn:limiting_mgale_problem} 
and~\eqref{eqn:limiting_mgale_variation}
    has a unique solution,
    then $(\eta^N_t)_{t \ge 0}$ converges weakly
to that solution
    as $N \to \infty$.
\end{corollary}
When $\alpha>0$, the limit points can be thought of as interacting superprocesses. For
example, when $r$ and $\gamma$ are constant, and 
$F(x,\eta_s)=1-\smooth{F} \eta_s(x)$,
we recover a superprocess with nonlinear death rates corresponding to logistic growth
\citep{etheridge:2004}
that is a continuous limit of the Bolker-Pacala model \citep{bolker/pacala:1997,bolker/pacala:1999}.
We are not aware of a general result to determine when we will have uniqueness of 
solutions to the martingale problem of Theorem~\ref{thm:nonlocal_convergence}
when $\alpha>0$.
However, the Dawson--Girsanov transform tells us that we have uniqueness in this special 
case of the superprocess with nonlinear death rates, and 
Perkins stochastic calculus (and its adaptation to a 
lookdown setting) provides uniqueness for cases with interactions in the 
dispersal mechanism of
the superprocess. We refer 
to~\cite{dawson:1993, perkins:1992}, and \cite{donnelly/kurtz:1999} 
for approaches to showing that these sorts of martingale problems are well-posed.

@@

\begin{proposition}
	\label{nonlocalPME to PME}
Suppose that
we can write $\rho_\gamma=\zeta*\check{\zeta}$, where $\check{\zeta}(x)=\zeta(-x)$ and
$\zeta\in\mathcal{S}(\IR^d)$ (the Schwartz space of rapidly decreasing functions).
Furthermore, suppose that %$\psi_0^\epsilon\in L^1(\IR^d)$, 
$\psi_0^\epsilon\geq 0$ is such that
there exist $\lambda\in (0,1)$ and $C\in (0,\infty)$ (independent
of $\epsilon$) such that 
\begin{equation*}
\int\exp(\lambda \|x\|)\psi_0^\epsilon(x)dx<C,\quad\mbox{ and }
\sup_\epsilon\int \psi_0^\epsilon|\log \psi_0^\epsilon|dx<\infty,
\end{equation*}
with
$\psi_0^\epsilon\rightharpoonup \psi_0$ as $\epsilon\to 0$. Then
writing $\psi^\epsilon$ for the solution to~(\ref{mollified equation})
on $[0,T]\times \IR^d$ with
initial condition $\psi_0^\epsilon$,
$\psi^\epsilon\rightharpoonup \psi$ as $\epsilon\to 0$ where
$\psi\in L_t^2(H^1)\cap C_t(L^1)$, $\int \psi|\log \psi| dx<\infty$, and
$\psi$ solves~(\ref{PME}) on $[0,T]\times \IR^d$. 
\end{proposition}
The example that we have in mind for the kernel $\rho_\gamma$ is a Gaussian kernel.
For the proof, see Section~\ref{sec:pme}.
\begin{remark}
Although it seems hard to formulate an all-encompassing result,
Propositions~\ref{prop:nonlocal_to_local} and~\ref{nonlocalPME to PME} are by no
means exhaustive. When the scaling limit is deterministic, one can 
expect analogous results under rather general conditions. However, when the limit
points are stochastic, they resemble ``nonlinear superprocesses'' and so one cannot
expect a density with respect to Lebesgue measure in $d\geq 2$. It is then not
reasonable to 
expect to be able to make sense of the limit if we scale the kernels in this way.
Moreover, in one dimension, where the classical superprocess does have a density with 
respect to Lebesgue measure, the form of~(\ref{eqn:limiting_mgale_problem})
suggests that even if one can remove the local averaging from $\gamma$, it
will be necessary
to retain averaging of $r$ in order to obtain a well-defined limit. 
\end{remark}

@@

We are interested in two questions.
First, when is the motion of an ancestral 
lineage, given complete knowledge of the population process, a well-defined process?
In other words, is knowledge of the process $(\eta_t)_{t=0}^T$ that records 
numbers of individuals
but not their ancestry sufficient to define the distribution of $(L_t)_{t=0}^T$?
Second, does the process have a tractable description?

@@

% % % % % % % % % % % % % % % %
\subsection{Lineage motion is not uniquely determined by population density}

@@

>>>>

\newif\ifsubmission
\submissiontrue
% \submissionfalse
\ifsubmission
    % % stuff for submission
    \usepackage{lineno}
    % allow line numbers around math environments
    % from https://tex.stackexchange.com/questions/43648/why-doesnt-lineno-number-a-paragraph-when-it-is-followed-by-an-align-equation
        \newcommand*\patchAmsMathEnvironmentForLineno[1]{%
          \expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
          \expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
          \renewenvironment{#1}%
             {\linenomath\csname old#1\endcsname}%
             {\csname oldend#1\endcsname\endlinenomath}}% 
        \newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
          \patchAmsMathEnvironmentForLineno{#1}%
          \patchAmsMathEnvironmentForLineno{#1*}}%
        \AtBeginDocument{%
        \patchBothAmsMathEnvironmentsForLineno{equation}%
        \patchBothAmsMathEnvironmentsForLineno{align}%
        \patchBothAmsMathEnvironmentsForLineno{flalign}%
        \patchBothAmsMathEnvironmentsForLineno{alignat}%
        \patchBothAmsMathEnvironmentsForLineno{gather}%
        \patchBothAmsMathEnvironmentsForLineno{multline}%
        }
\else
    % for the nice version
\fi

% Responses to reviews
\input{review-response-commands}
% set this to show line numbers and include responses to reviews or not
\newif\ifreviewresponses
\reviewresponsestrue  % include them
% \reviewresponsesfalse  % don't include them
\newcommand{\responsefile}{review-responses}  % name of the review responses file

@@

We shall write $\mu_\theta(x, X/N)$ for the per-capita death rate of mature individuals
in the population.
In order for the 
population density to change over timescales of order $\theta$, we should like the net 
per capita reproductive rate 
to scale as $1/\theta$. 
In classical models, in which $r$, $\gamma$, and $\mu$ are constant, 
this quantity is simply $r\gamma -\mu$. 
Here, because production of juveniles and their establishment are
mediated by population density measured relative to different points, 
the net reproductive rate will take a more complicated form. 
In particular, the total rate of production of mature offspring by an individual at $x$ will be
\begin{equation} \label{eqn:total_repro}
	\gamma\big(x,\smooth{\gamma}X(x)/N\big)\int r\big(y, \smooth{r}X(y)/N\big)q_{\theta}(x,dy).
\end{equation}
Nonetheless, it will be convenient to define the death rate $\mu_\theta$ in terms of 
its deviation from $r\gamma$. 
To this end, we define
the death rate of an individual at $x$ to be \revpoint{1}{4}
\begin{align} \label{eqn:mu_defn}
    \mu_\theta(x)
    =
    \max\left\{0, 
        r(x, \smooth{r} X(x) / N) \gamma(x, \smooth{\gamma} X(x) / N)
        - \frac{1}{\theta} F(x, \smooth{F} X(x) / N)
    \right\} ,
\end{align}
where this equation defines $F(x, m) : \IR^d \times \IR_{\ge 0} \to \IR$,
and $\rho_F$ is again a smooth kernel. 
The function $F$ is nearly
the net per capita reproductive rate, scaled by $\theta$,
and would be equal to it in a nonspatial model;
but, as can be seen from \eqref{eqn:total_repro},
differs because an offspring's establishment probability is measured at their new location
rather than that of their parent.
For the most part, we work with $F$ instead of $\mu_\theta$.

@@

In summary, at each time $t$, $\eta^N_t$ is purely atomic, consisting of atoms of mass $1/N$
(which are the individuals).
At instantaneous rate $\theta \gamma(x, \eta^N_t) N \eta^N_t(dx)$ an offspring of mass $1/N$ is 
produced at location $x$; it disperses to 
a location $y$ offset from $x$
by an independent Gaussian random variable with mean $\meanq(x) / \theta$ \revpoint{1}{6}
and covariance matrix $\covq(x) / \theta$,
and once there establishes instantaneously \revpoint{1}{5}
with probability $r(y, \eta^N_t)$, or else dies. 
At instantaneous rate $\theta \mu_\theta(x, \eta^N_t) N \eta^N_t(dx)$ an individual at location 
$x$ dies.
Note that the process 
$\left(\eta^N_t\right)_{t\ge 0}$, which
records numbers and locations of adult individuals, is just a scaled spatial birth and 
death process. If, for example, we insist that $\gamma(x,m)$ is bounded, then 
existence (and in particular non-explosion) is guaranteed by comparison with
a pure birth process. We do not dwell on this, as we shall require more stringent conditions
if we are to pass to the limit as $\theta$ and $N$ tend to infinity.

@@

\begin{remark}
\label{ancestral lineages: first guess} \revpoint{1}{7}
An equivalent way to describe the model would be to say that
when the state of the population is $\eta$,
an individual at $x$ gives birth at rate
$$
    \theta \gamma(x, \eta)
    \int r(y, \eta) q(x, dy) ,
$$
and that offspring disperse according to the kernel
$$
    q_\theta^\mathfrak{m}(x,\eta,dy)
    :=
    \frac{
        r(y, \eta) q_\theta(x, dy)
    }{
        \int r(z, \eta) q_\theta(x, dz)
    } .
$$
Clearly, the random walk driven by this dispersal kernel
is biased towards regions of higher establishment probability.
For comparison with future results,
it is interesting to write down the limiting generator:
\begin{align}
	\label{weighted dispersal}
    \lim_{\theta \to \infty}
    \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, \eta, dy)
    &=
    \frac{
        \DG\left[ f(\cdot) r(\cdot, \eta) \right](x)
        - 
        f(x) \DG\left[ r(\cdot, \eta) \right](x)
    }{
        r(x, \eta^{N})
    } .
\end{align}
In the simplest case of unbiased isotropic dispersal
(i.e.,~$\meanq = 0$ and $\covq = I$), $\DG = \Delta$,
and so~(\ref{weighted dispersal}) is equal to
\begin{align*}
    \Delta f(x) + 2 \grad f(x) \cdot \grad \log r(\cdot, \smooth{r} \eta(\cdot))(x) .
\end{align*}
One might guess that the spatial motion described by following  
the ancestral lineage of an individual 
back through time
would be described (in the limit) by the adjoint of this generator.
However, we will see in Section~\ref{sec:ancestral lineages}
that this is not in fact the case.
\end{remark}

@@

{\bf Reproduction parameters:}
We assume that 
\begin{enumerate}
            \addtocounter{enumi}{2}
\item The function $F(x,m)$ satisfies 
    \begin{enumerate}
    \item $F(x,m)$ is locally Lipschitz in $m$;
    \item $F(x,m)$ is uniformly bounded above (but not necessarily below);
    \item for each fixed $m$, $\sup_{x\in\IR^d}\sup_{k\leq m}|F(x,k)|<\infty$;
    \end{enumerate}
\item The functions $r(x,m)$, $\gamma(x,m)$ have bounded first and second 
    derivatives in both arguments;
    \label{r_gamma_derivs_condition}
\item $\gamma(x,m)$ is uniformly bounded;
    \label{gamma_bounded_condition}
\item For each $f \in C_b^2(\IR^d)$,
    there is a $C_f$ such that
    $$
        |\gamma(x, \eta) \theta \int 
        (r(y,\eta) f(y) - r(x, \eta) f(x))
        q_\theta(x, dy)| \le C_f (1 + |f(x)|)
    $$
    for all $x \in \IR^d$ and $\eta \in \measures$.
    Furthermore, $C_f$ only depends on the norm of the first two derivatives of $f$,
    i.e., 
    \[
        C_f = C(\sup_x \sup_{\|z\|=1} \max( \sum_i z_i \partial_{x_i} f(x), \sum_{ij} z_i z_j \partial_{x_i x_j} f(x))) .
    \] \label{gamma_B_condition} \revpoint{1}{9}
\end{enumerate}
To keep expressions manageable, we shall also assume that  \revpoint{1}{1}
\[
\mu_\theta(x) = r(x,\eta) \gamma(x,\eta) - \frac{1}{\theta} F(x,\eta),
\]
that is, this expression is non-negative so that there is no need to take the maximum
	with zero in~(\ref{eqn:mu_defn}). (This is anyway true for 
	sufficiently large $\theta$.)
\end{assumptions}

@@

The purpose of the conditions that we have placed on the reproduction parameters is to 
ensure that the net per capita reproduction rate (before time scaling)
is order $1/\theta$. As remarked above, 
because of the non-local reproduction mechanism, it no longer suffices \revpoint{1}{10}
to assume that 
$r(x,\eta)\gamma(x,\eta)-\mu_\theta(x)$ is of order $1/\theta$.
Perhaps the simplest example in which we can see this
is the case where $\gamma \equiv 1$ and $F \equiv 0$, so that $\mu_\theta = r$,
and $\eta = \delta_x$
(i.e., the population has all individuals at a single location),
so that $\smooth{r} \eta(y) = \rho_r(y)$.
In this case, the mean rate of change of the total population size
is $\int (r(y, \rho_r(y) ) - r(x, \rho_r(x))) q_\theta(x, dy)$;
the first condition of Lemma~\ref{lem:conditions on r} would ensure this is of order $1/\theta$.

@@

\begin{corollary} \label{cor:superprocess_uniqueness}
    Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
    if the martingale problem
    defined by equations~\eqref{eqn:limiting_mgale_problem} 
and~\eqref{eqn:limiting_mgale_variation}
    has a unique solution,
    then $(\eta^N_t)_{t \ge 0}$ converges weakly
to that solution
    as $N \to \infty$.
\end{corollary}
When $\alpha>0$, the limit points can be thought of as interacting superprocesses. For
example, when $r$ and $\gamma$ are constant, and 
$F(x,\eta_s)=1-\smooth{F} \eta_s(x)$,
we recover a superprocess with nonlinear death rates corresponding to logistic growth
\citep{etheridge:2004}
that is a continuous limit of the Bolker-Pacala model \citep{bolker/pacala:1997,bolker/pacala:1999}.
We are not aware of a general result to determine when we will have uniqueness of 
solutions to the martingale problem of Theorem~\ref{thm:nonlocal_convergence}
when $\alpha>0$.
However, the Dawson--Girsanov transform tells us that we have uniqueness \revpoint{1}{12}
in this special case of the superprocess with nonlinear death rates, and 
Perkins stochastic calculus (and its adaptation to a 
lookdown setting) provides uniqueness for cases with interactions in the 
dispersal mechanism of
the superprocess. We refer 
to~\cite{dawson:1993, perkins:1992}, and \cite{donnelly/kurtz:1999} 
for approaches to showing that these sorts of martingale problems are well-posed.

@@

\begin{proposition}
	\label{nonlocalPME to PME}
Suppose that
we can write $\rho_\gamma=\zeta*\check{\zeta}$, where $\check{\zeta}(x)=\zeta(-x)$ and
$\zeta\in\mathcal{S}(\IR^d)$ (the Schwartz space of rapidly decreasing functions).
Furthermore, suppose that %$\psi_0^\epsilon\in L^1(\IR^d)$, 
$\psi_0^\epsilon\geq 0$ is such that
there exist $\lambda\in (0,1)$ and $C\in (0,\infty)$ (independent
of $\epsilon$) such that 
\begin{equation*}
\int\exp(\lambda \|x\|)\psi_0^\epsilon(x)dx<C,\quad\mbox{ and }
\sup_\epsilon\int \psi_0^\epsilon|\log \psi_0^\epsilon|dx<\infty,
\end{equation*}
with
$\psi_0^\epsilon\rightharpoonup \psi_0$ as $\epsilon\to 0$. Then
writing $\psi^\epsilon$ for the solution to~(\ref{mollified equation})
on $[0,T]\times \IR^d$ with
initial condition $\psi_0^\epsilon$,
$\psi^\epsilon\rightharpoonup \psi$ as $\epsilon\to 0$ where
$\psi\in L_t^2(H^1)\cap C_t(L^1)$, $\int \psi|\log \psi| dx<\infty$, and
$\psi$ solves~(\ref{PME}) on $[0,T]\times \IR^d$. 
\end{proposition}

The example that we have in mind for the kernel $\rho_\gamma$ is a Gaussian kernel.
For the proof, see Section~\ref{sec:pme}.

\begin{remark} \label{remark_on_nonlocal_to_local}
Although it seems hard to formulate an all-encompassing result,
Propositions~\ref{prop:nonlocal_to_local} and~\ref{nonlocalPME to PME} are by no
means exhaustive. When the scaling limit is deterministic, one can 
expect analogous results under rather general conditions. However, when the limit
points are stochastic, they resemble ``nonlinear superprocesses'' and so one cannot
expect a density with respect to Lebesgue measure in $d\geq 2$. It is then not
reasonable to 
expect to be able to make sense of the limit if we scale the kernels in this way.
Moreover, in one dimension, where the classical superprocess does have a density with 
respect to Lebesgue measure, the form of~(\ref{eqn:limiting_mgale_problem})
suggests that even if one can remove the local averaging from $\gamma$, it
will be necessary
to retain averaging of $r$ in order to obtain a well-defined limit. 
\end{remark}

@@

We are interested in two questions.
First, when is the motion of an ancestral 
lineage, given complete knowledge of the population process, a well-defined process?
In other words, is knowledge of the process $(\eta_t)_{t=0}^T$ that records 
numbers of individuals
but not their ancestry sufficient to define the distribution of $(L_t)_{t=0}^T$? \revpoint{1}{15}
Second, does the process have a tractable description?

@@

% % % % % % % % % % % % % % % %
\subsection{Lineage motion is not uniquely determined by population density}
\label{sec:nonunique_lineage}

@@

% reviews here if toggled above
\includereviews
